Carbonate chemistry at Ny-Ålesund

### 2021-05-27 awipev-CO2.Rmd
still on deconvolution

## Deconvolution of pCO2 changes
```{r pCO2 changes due to changes in T, S, AT and CT, include=FALSE}
# We follow the method of Garcia-Ibanez described above.
# construct a dataframe with monthly means for the entire series (mXX) as well as real data (without mrefix m)
deconv_dat <- tbl_df(
  data.frame(date=as.POSIXct(mean0m$sampling_date), mAT=means_month0m$AT[mean0m$monthd]*1e-6, mCT=means_month0m$CT[mean0m$monthd]*1e-6, mS=means_month0m$Salinity[mean0m$monthd], mT=means_month0m$Temperature[mean0m$monthd], P=mean0m$mean_P, Pt=mean0m$mean_Pt, Sit=mean0m$mean_Sit, AT=mean0m$mean_ta*1e-6, CT=mean0m$mean_dic*1e-6, S=mean0m$mean_salinity, T=mean0m$mean_temperature)
)

@@

## Deconvolution of pCO2 changes
```{r pCO2 changes due to changes in T, S, AT and CT, include=FALSE}
# First we prepare data. CT is needed for deconvolution
# we calculate it from at_calc and pCO2
# nuts are not taken into consideration
deconv_dat <- d_all %>% # just for this chunk
  dplyr::select(datetime, sal_fb, temp_fb, pco2_fb, at_calc) %>% 
  dplyr::mutate(ct_calc = seacarb::carb(
    flag = 24, var1 = pco2_fb, var2 = at_calc, S=sal_fb, T=25, Patm=1, P=0, Pt=0, Sit=0,
        k1k2="x", kf="x", ks="d", pHscale="T", b="u74", gas="potential", 
        warn="y", eos="eos80", long=1.e20, lat=1.e20)

  ))

>>>>

## Deconvolution of pCO2 changes
```{r pCO2 changes due to changes in T, S, AT and CT, include=FALSE}
# First we prepare data. CT is needed for deconvolution
# we calculate it from at_calc and pCO2
# nuts are not taken into consideration
deconv_tmp <- d_all %>% # just for this chunk
  dplyr::select(datetime, monthd, sal_fb, temp_fb, pco2_fb, at_calc) %>% 
  tidyr::drop_na() %>% 
  dplyr::mutate(ct_calc = seacarb::carb(
    flag = 24, var1 = deconv_tmp$pco2_fb, var2 = deconv_tmp$at_calc*1e-6, S=deconv_tmp$sal_fb, T=deconv_tmp$temp_fb, 
    Patm=1, P=1.1, Pt=0, Sit=0, 
    k1k2="l", kf="dg", ks="d", pHscale="T", b="u74")
    )
deconv_monthly <-  deconv_tmp %>% 
  dplyr::group_by(monthd) %>% 
  dplyr::summarise(
    sal_fb = mean(sal_fb, na.rm = TRUE),
    temp_fb = mean(temp_fb, na.rm = TRUE),
    pco2_fb = mean(pco2_fb, na.rm = TRUE),
    at_calc = mean(at_calc, na.rm = TRUE),
    ct_calc = mean(ct_calc, na.rm = TRUE)
  ) %>% 
  dplyr::ungroup()

deconv_dat <- tbl_df(
  data.frame(date=as.POSIXct(mean0m$sampling_date), mAT=means_month0m$AT[mean0m$monthd]*1e-6, mCT=means_month0m$CT[mean0m$monthd]*1e-6, mS=means_month0m$Salinity[mean0m$monthd], mT=means_month0m$Temperature[mean0m$monthd], P=mean0m$mean_P, Pt=mean0m$mean_Pt, Sit=mean0m$mean_Sit, AT=mean0m$mean_ta*1e-6, CT=mean0m$mean_dic*1e-6, S=mean0m$mean_salinity, T=mean0m$mean_temperature)
)

@@

## Deconvolution of pCO2 changes
```{r pCO2 changes due to changes in T, S, AT and CT, include=FALSE}
# First we prepare data. CT is needed for deconvolution
# we calculate it from at_calc and pCO2
# nuts are not taken into consideration
deconv_tmp <- d_all %>% # just for this chunk
  dplyr::select(datetime, monthd, sal_fb, temp_fb, pco2_fb, at_calc) %>% 
  dplyr::mutate(ct_calc = seacarb::carb(
    flag = 24, var1 = pco2_fb, var2 = at_calc, S=sal_fb, T=25, Patm=1, P=0, Pt=0, Sit=0,
        k1k2="l", kf="dg", ks="d", pHscale="T", b="u74", gas="potential", 
        warn="y", eos="eos80", long=1.e20, lat=1.e20)
    )
deconv_monthly <-  d_all %>% 
  dplyr::group_by(monthd) %>% 
  dplyr::summarise(
    sal_fb = mean(sal_fb, na.rm = TRUE),
    temp_fb = mean(temp_fb, na.rm = TRUE),
    pco2_fb = mean(pco2_fb, na.rm = TRUE),
    at_calc = mean(at_calc, na.rm = TRUE),
    ct_calc = mean(ct_calc, na.rm = TRUE)
  ) %>% 
  ungroup()
